Enforced Invariant Confluence

### 2016-11-27 doc/counters.tex
Fixed up some figures.
Added TODO.

A set of transactions $T$ is \iconfluent{} with respect to invariant $I$ if for
all database states $D$ and chains $C_1$ and $C_2$ created from $T$, if $D$
satisfies $I$, $C_1$ satisfies $I$ starting at $D$, and $C_2$ satisfies $I$
starting at $D$, then $D \circ C_1 \circ C_2$ satisfies $I$.

@@

  \begin{tikzpicture}
    \node[] (0-isafety) at (0, 0) {0-\isafety};
    \node[below=of 0-isafety]     (1-isafety)      {1-\isafety};
    \node[below=of 1-isafety]     (k-isafety)      {$k$-\isafety};
    \node[right=of 0-isafety]     (istrengthstar)  {\istrengthstar};
    \node[above=of istrengthstar] (ipreservation)  {\ipreservation};
    \node[right=of istrengthstar] (iconfluence)    {\iconfluence};
    \node[below=of iconfluence]   (k-iconfluence)  {$k$-\iconfluence};
    \node[below=of k-iconfluence] (1-iconfluence)  {1-\iconfluence};
    \node[below=of istrengthstar] (istrength)      {\istrength};
    \node[below=of istrength]     (1-iconvergence) {1-\iconvergence};

@@

  \caption{
    An illustration of the relationship between various \iconfluence{}
    alternatives. We have proven bold implications in both directions. For
    example, we have proven both \iconfluence $\protect \centernot \implies$
    \istrengthstar.
  }
  \label{fig:iconfluence-alternatives}
\end{figure}

@@

  \caption{
    An illustration of \iconfluence{} alternatives. \todo{Describe drawings.}
  }
  \label{fig:iconfluence-alternatives}
\end{figure}

>>>>

A set of transactions $T$ is \iconfluent{} with respect to invariant $I$ if for
all database states $D$ and chains $C_1$ and $C_2$ created from $T$, if $D$
satisfies $I$, $C_1$ satisfies $I$ starting at $D$, and $C_2$ satisfies $I$
starting at $D$, then $D \circ C_1 \circ C_2$ satisfies $I$.
\todo{
  This isn't quite the definition of \iconfluence{} Bailis uses. Ponder whether
  this simpler definition is okay.
}

@@

\tikzstyle{automatable}=[fill=green!20]
\tikzstyle{intractable}=[fill=red!20]
\begin{figure}[h]
  \centering

  \begin{tikzpicture}
    \node[automatable] (0-isafety) at (0, 0) {0-\isafety};
    \node[automatable, below=of 0-isafety]     (1-isafety)      {1-\isafety};
    \node[automatable, below=of 1-isafety]     (k-isafety)      {$k$-\isafety};
    \node[intractable, right=of 0-isafety]     (istrengthstar)  {\istrengthstar};
    \node[automatable, above=of istrengthstar] (ipreservation)  {\ipreservation};
    \node[intractable, right=of istrengthstar] (iconfluence)    {\iconfluence};
    \node[automatable, below=of iconfluence]   (k-iconfluence)  {$k$-\iconfluence};
    \node[automatable, below=of k-iconfluence] (1-iconfluence)  {1-\iconfluence};
    \node[automatable, below=of istrengthstar] (istrength)      {\istrength};
    \node[automatable, below=of istrength]     (1-iconvergence) {1-\iconvergence};

@@

  \caption{
    An illustration of the relationship between various \iconfluence{}
    alternatives. We have proven bold implications in both directions. For
    example, we have proven both \istrengthstar{} $\implies$ \iconfluence{} and
    \iconfluence{} $\protect \centernot \implies$ \istrengthstar{}. Conditions
    shaded green can be automatically determined using an SMT solver.
    Conditions shaded red are not easy to automatically determine.
  }
  \label{fig:iconfluence-alternatives-implications}
\end{figure}

@@

  \caption{
    An illustration of \iconfluence{} alternatives. \todo{Describe drawings.}
  }
  \label{fig:iconfluence-alternatives-diagrams}
\end{figure}
